---
title: "YouTube Data Collection and Sentiment Analysis"
author: "Tori Green"
date: "2025-05-05"
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: flatly
---

## 🎯 Project Overview

This project demonstrates how to use R to:  
- Collect video data and comments from YouTube using the `tuber` package.  
- Analyze comments with text mining and sentiment analysis.  
- Create visualizations including a word cloud and sentiment bar plot.

---

## 📦 Setup & Authentication

```{r message=FALSE, warning=FALSE}
# Install packages if needed
# install.packages(c("tuber", "tm", "SnowballC", "wordcloud", "syuzhet"))

library(tuber)
library(tm)
library(SnowballC)
library(wordcloud)
library(syuzhet)
```

### 🔑 API Authentication

> ⚠️ **Important:** Replace with your own YouTube API credentials from the Google Cloud Console.

```{r}
client_id <- Sys.getenv("YT_CLIENT_ID")     # Set your YouTube API client ID
client_secret <- Sys.getenv("YT_CLIENT_SECRET") # Set your YouTube API client secret
yt_oauth(client_id, client_secret, token = '')

```

---

## 📂 Data Collection

### ▶️ Get Video Stats & Details

```{r}
get_stats(video_id = "SHTySDvxHhY")
get_video_details(video_id = "SHTySDvxHhY")
```

### 🔍 Search for Videos

```{r}
search_result <- yt_search("Social Media Analytics")
head(search_result, 10)   # show first 10 results
```

### 💬 Collect Video Comments

```{r}
comments <- get_all_comments(video_id = "SHTySDvxHhY")
head(comments)
```

💾 **Save comments to CSV for later use**
```{r}
write.csv(comments, file = "YouTubeVideoComments.csv", row.names = FALSE)
```

---

## 📝 Text Processing & Word Cloud

### 📑 Create Comments Corpus

```{r}
comments_corp <- Corpus(VectorSource(comments$textOriginal))
```

### 🧹 Clean & Create Document-Term Matrix

```{r}
comments_DTM <- DocumentTermMatrix(comments_corp,
                                   control = list(removePunctuation = TRUE,
                                                  removeNumbers = TRUE,
                                                  stopwords = TRUE))
# Preview
as.matrix(comments_DTM[1:5, 1:5])
```

### ☁️ Word Cloud of Comments

```{r}
comments_terms <- colSums(as.matrix(comments_DTM))
wordcloud(words = names(comments_terms),
          freq = comments_terms,
          min.freq = 2,
          colors = brewer.pal(8, "Dark2"))
```

---

## 💡 Sentiment Analysis

### 🔍 NRC Sentiment Scores

```{r}
video_sentiment <- get_nrc_sentiment(as.character(comments$textOriginal))
head(video_sentiment)
```

### 📊 Summarize Emotion Counts

```{r}
VideoCommentsEmotionsDFCount <- data.frame(
  Emotion = colnames(video_sentiment),
  Frequency = colSums(video_sentiment > 0)
)

# Bar plot
barplot(VideoCommentsEmotionsDFCount$Frequency,
        names.arg = VideoCommentsEmotionsDFCount$Emotion,
        main = "YouTube Video Comments Sentiment",
        xlab = "Emotions", ylab = "Frequency", las = 2,
        col = rainbow(10))
```

### ➕ Comment Polarity

```{r}
VideoCommentPolarity <- data.frame(
  Comment = as.character(comments$textOriginal),
  Polarity = get_sentiment(as.character(comments$textOriginal))
)
head(VideoCommentPolarity)
```

---

## ✅ Key Insights

- Word cloud highlights most frequent discussion terms in the video’s comments.  
- Sentiment analysis provides a breakdown of emotions like joy, anticipation, and trust.  
- Polarity analysis assigns each comment a score showing if it’s positive or negative.

